Analysis of Information Security Job Advertisements

### 2020-05-24 paper/paper.tex
Add empty sections.
Finish data extraction part.

The first contender we found was \textit{OctoParse}, which provides a desktop application for scraping. Its free tier allows scraping unlimited pages on unlimited computers, with two concurrent scraping jobs. It allows configuring 10 different crawler configurations. There was, however, one major drawback to using \textit{OctoParse}: Its slogan claims “Easy Web Scraping for Anyone” – “Anyone” in this context meaning anyone with a Windows computer, since the desktop application is only supported on Windows. Linux and macOS users would have to run a virtual machine in order to use it, which is definitely not a viable solution for scraping a few websites. So we began looking for alternatives.

One alternative we found was \textit{ScrapingBot}. Unlike \textit{OctoParse}, which provides a desktop application, \textit{ScrapingBot} does not provide an application at all. It is meant to be used similarly to using a proxy server. You can make an HTTP request with the same URL you normally would, and it responds with the contents, which includes any rendered JavaScript. Its free plan includes 100 API calls per month, therefore this also was no viable solution either, since the API calls would probably have been used up before the scraper was even working properly.

The next service we found was \textit{ScrapeStorm}, which is very similar to \textit{OctoParse} in terms of what it provides. It offers a desktop application which works on Linux, macOS as well as Windows. In that regard, it was already looking like a better solution \textit{OctoParse}. The free plan allows 10 different crawler configurations and 1 concurrent local run. It also allows 100 exported rows per day, either into a file or directly into a database. All in all, \textit{ScrapeStorm} seemed like a good fit.

After choosing \textit{ScrapeStorm}, we started by setting up the crawlers. The websites we wanted to scrape are \texttt{monster.at}, \texttt{at.indeed.com} and \texttt{stepstone.at}.

@@

With this setback, we now had to find another way to scrape this data. After taking a second look at the \textit{ScrapingBot} homepage, we saw that it is using headless \textit{Chrome} for its backend. We decided to venture further into this direction and found \textit{Selenium}, which can be used to programmatically use a web browser.

\textit{Selenium} supports all of the major web browsers, the only thing you need is the so called “webdriver” for the corresponding browser. Additionally, \textit{Selenium} can be used with a wide array of programming languages. For our purposes we chose to go with the Ruby version of \textit{Selenium}. Specifically, we chose to use \textit{Rake}, which is similar to \textit{Make}, since it allows us to use the full functionality of \textit{Ruby} and specify tasks for each website. These scraping tasks can then be run with a simple \texttt{rake} command.

@@

The first thing we needed to determine for \textit{Monster} was how to perform searches. For this, we simply made a search request manually in a web browser. With the search string “information security” immediately noticed that it was escaped as \texttt{information-security} rather than the standard way to escape HTML, i.e. \texttt{information\%20security}. We needed to consider this when building the query URL.

@@

For \textit{Indeed}, the initial step to implement proper scraping was to implement fetching search results. Luckily, unlike on \textit{Monster}, the search string could be escaped as \texttt{information\%20security} using standardised HTML escape codes.

@@

Implementing the gathering of search results on \textit{StepStone} was largely similar to the workflow used for \textit{Indeed}. The search string can be escaped using the standardised HTML escape codes, furthermore there are some query parameters we make use of: The \texttt{fu} parameter can be used to set the job category. We used \texttt{1000000} for this parameter to specify the “IT \& Communications” category. For faster scraping, we also set the \texttt{li} parameter to \texttt{100} in order to display 100 results per page rather than the default 25. Finally, we use the \texttt{of} parameter to specify the result offset which is then used in the same way as for \texttt{Indeed}. \textit{StepStone} displays the pagination controls at the top of the results page. These include the current as well as the last page number. Using this information we can stop the loop once we reach the last page.

@@

After a couple of scraping runs, we noticed that there were duplicate results. This happened for all three websites. These duplicates were either completely equal or had only minor differences in their HTML source code. Nevertheless, we needed to introduce a post-processing step after the scraping is finished. We implemented a new \textit{Rake} task called \texttt{deduplicate} which reads all results and sorts them by date. We then convert the results' title and HTML body content to plain text and group the results according to that. Finally, we select all results with more than one source file and remove all but the latest one.

@@

With these two types the extraction rate was now at approximately 90\%. A few more results could be detected by extracting the word \texttt{'studium'}, since some job advertisements refer to a bachelor's degree simply as “abgeschlossenes Studium” (completed studies).

@@

>>>>

The first contender we found was \textit{OctoParse} \cite{octoparse}, which provides a desktop application for scraping. Its free tier allows scraping unlimited pages on unlimited computers, with two concurrent scraping jobs. It allows configuring 10 different crawler configurations. There was, however, one major drawback to using \textit{OctoParse}: Its slogan claims “Easy Web Scraping for Anyone” – “Anyone” in this context meaning anyone with a Windows computer, since the desktop application is only supported on Windows. Linux and macOS users would have to run a virtual machine in order to use it, which is definitely not a viable solution for scraping a few websites. So we began looking for alternatives.

One alternative we found was \textit{ScrapingBot} \cite{scrapingbot}. Unlike \textit{OctoParse}, which provides a desktop application, \textit{ScrapingBot} does not provide an application at all. It is meant to be used similarly to using a proxy server. You can make an HTTP request with the same URL you normally would, and it responds with the contents, which includes any rendered JavaScript. Its free plan includes 100 API calls per month, therefore this also was no viable solution either, since the API calls would probably have been used up before the scraper was even working properly.

The next service we found was \textit{ScrapeStorm} \cite{scrapestorm}, which is very similar to \textit{OctoParse} in terms of what it provides. It offers a desktop application which works on Linux, macOS as well as Windows. In that regard, it was already looking like a better solution \textit{OctoParse}. The free plan allows 10 different crawler configurations and 1 concurrent local run. It also allows 100 exported rows per day, either into a file or directly into a database. All in all, \textit{ScrapeStorm} seemed like a good fit.

After choosing \textit{ScrapeStorm}, we started by setting up the crawlers. The websites we wanted to scrape are \texttt{monster.at} \cite{monster}, \texttt{at.indeed.com} \cite{indeed} and \texttt{stepstone.at} \cite{stepstone}.

@@

With this setback, we now had to find another way to scrape this data. After taking a second look at the \textit{ScrapingBot} homepage, we saw that it is using headless \textit{Chrome} for its backend. We decided to venture further into this direction and found \textit{Selenium} \cite{selenium}, which can be used to programmatically use a web browser.

\textit{Selenium} supports all of the major web browsers, the only thing you need is the so called “webdriver” for the corresponding browser. Additionally, \textit{Selenium} can be used with a wide array of programming languages. For our purposes we chose to go with the Ruby version of \textit{Selenium}. Specifically, we chose to use \textit{Rake} \cite{rake}, which is similar to \textit{Make}, since it allows us to use the full functionality of \textit{Ruby} \cite{ruby} and specify tasks for each website. These scraping tasks can then be run with a simple \texttt{rake} command.

@@

The first thing we needed to determine for \textit{Monster} \cite{monster} was how to perform searches. For this, we simply made a search request manually in a web browser. With the search string “information security” immediately noticed that it was escaped as \texttt{information-security} rather than the standard way to escape HTML, i.e. \texttt{information\%20security}. We needed to consider this when building the query URL.

@@

For \textit{Indeed} \cite{indeed}, the initial step to implement proper scraping was to implement fetching search results. Luckily, unlike on \textit{Monster}, the search string could be escaped as \texttt{information\%20security} using standardised HTML escape codes.

@@

Implementing the gathering of search results on \textit{StepStone} \cite{stepstone} was largely similar to the workflow used for \textit{Indeed}. The search string can be escaped using the standardised HTML escape codes, furthermore there are some query parameters we make use of: The \texttt{fu} parameter can be used to set the job category. We used \texttt{1000000} for this parameter to specify the “IT \& Communications” category. For faster scraping, we also set the \texttt{li} parameter to \texttt{100} in order to display 100 results per page rather than the default 25. Finally, we use the \texttt{of} parameter to specify the result offset which is then used in the same way as for \texttt{Indeed}. \textit{StepStone} displays the pagination controls at the top of the results page. These include the current as well as the last page number. Using this information we can stop the loop once we reach the last page.

@@

After a couple of scraping runs, we noticed that there were duplicate results. This happened for all three websites. These duplicates were either completely equal or had only minor differences in their HTML source code. Nevertheless, we needed to introduce a post-processing step after the scraping is finished. We implemented a new \textit{Rake} task called \texttt{deduplicate} which reads all results and sorts them by date. We then convert the results' title and HTML body content to plain text and group the results according to that. Finally, we can find all duplicates by selecting all results with more than one entry in the corresponding group and remove all but the latest one.

@@

With these two types the extraction rate was now at approximately 90\%. A few more results could be detected by extracting the words \texttt{'studium'} and \texttt{'universität'}/\texttt{'university'}, since some job advertisements refer to a bachelor's degree simply as “abgeschlossenes Studium” (completed studies) or list “Universität”/“University” as a requirement.

\subsubsection{Extracting the Type of Employment}
\label{subsub:extracting_the_type_of_employment}

We also wanted to know what type of employment a particular job advertisement pertains to, i.e. whether it is a full-time or part-time position and whether the contract is permanent or temporary. Some websites include this information in their metadata section, for others we would have to extract this data from the body text. Apart from the obvious keywords such as \texttt{'full-time'} and \texttt{'part-time'}, we also needed to look for the number of work hours per week in the body text, since some advertisements list the work hours explicitly instead of the more vague distinction between full-time and part-time. To extract this, we used a similar pattern to the one for extracting salaries: We loop through all pairs of words. If the first word is a number and the second word is either \texttt{'wochenstunden'} or \texttt{'hours'}, we parse the number. We assume \texttt{'full-time'} if that number is greater than 20, otherwise we assume \texttt{'part-time'}.

\subsubsection{Extracting the Location}
\label{subsub:extracting_the_location}

The next data point we needed to extract is the location of the job in question. Fortunately, all of the scraped websites include the location as a separate field in their respective metadata section. This way, we could limit our extraction to just this field. This field required a specialised data cleaning step which expands state acronyms. For example, we needed to replace \texttt{'W'} with \texttt{'Wien'} or \texttt{'Oö'} and \texttt{'OÖ'} with \texttt{'Oberösterreich'}. Additionally, we also replaced the English translations of states and used the German spelling as the canonical version.

Furthermore, we used a database containing all major cities in Austria \cite{austria_cities_database} in order to also catch cases where only the city is specified but the corresponding state is missing. With this database, we can then map the tokenised string to cities and states. In the end, we get a list of all extracted cities and another list of all extracted states. In case we are not able to extract anything from the metadata field, we fall back to running the same extraction function on the whole body text.

\subsubsection{Extracting of Certifications}
\label{subsub:extracting_of_certifications}

Up next was the extraction of certifications. We found an article listing the most prominent certifcations of the year 2020 \cite{certifications}. Incidentally, the authors of this article also retrieved this list from performing a job board survey. Using the list of certifications mentioned in the article and a manual review of the scraped data, we came up with a list (as can be seen in \autoref{certifications_table}) of all the certifications we wanted to extract.

\begin{table}[h]
  \caption{List of extracted certifications.}
  \label{certifications_table}

  \begin{tabular}{|l|l|}
    \hline
    \textbf{Certification} & \textbf{Description}                                \\ \hline
    CEH                    & Certified Ethical Hacker                            \\ \hline
    CISA                   & Certified Information Security Auditor              \\ \hline
    CISM                   & Certified Information Security Manager              \\ \hline
    CISSP                  & Certified Information Systems Security Professional \\ \hline
    CRISC                  & Certified in Risk and Information Systems Control   \\ \hline
    ITIL                   & Information Technology Infrastructure Library       \\ \hline
    CIA                    & Certified Internal Auditor                          \\ \hline
    ISO/IEC 27001          & Information Technology Security Techniques          \\ \hline
    HITRUST                & HITRUST Compliance Certification                    \\ \hline
    COBIT                  & COBIT Certification                                 \\ \hline
    ISO/IEC 22301          & Business Continuity Management                      \\ \hline
    CGEIT                  & Certified in the Governance of Enterprise IT        \\ \hline
    GIAC                   & GIAC Cybersecurity Certification                    \\ \hline
  \end{tabular}
\end{table}

In comparison to the other extraction tasks, extracting certifications was straight-forward given this fixed list. There was, however, still one adjustment needed for the data cleaning step with regards to the ISO/IEC certifications since some of them only specified \texttt{'ISO'} while others specified \texttt{'ISO/IEC'}. A few of them were also missing whitespace between the acronym and the number, e.g. \texttt{'ISO27001'}. For this reason, we added another regular expression replacement to the data cleaning step which normalises all of these occurrences to the canonical \texttt{'ISO/IEC \#\#\#\#\#'} form.

@@

\section{Findings}
\label{sec:findings}

\section{Conclusion}
\label{sec:conclusion}
